Eval expressions

### 2021-01-20 analysis/expressions.Rmd
Constant folding on strings

```{r}
canonic_expr <- function(exp) {
  if (is.call(exp)) {
    function_name <- exp[[1]]
    function_args <- exp[-1]
    res <- map(function_args, canonic_expr)
    # Function_name can be larger than one is a function with a namespace stats::model or another higher-order function
    # For instance, (function(x, y) x + y)(3, 4)
    if (length(function_name) == 1 && as.character(function_name) %in% arith_func && every(res, function(v) {
      v == "NUM"
    })) {
      return("NUM")
    }
    else if (length(function_name) == 1 && function_name == "::") {
      str_c(as.character(function_args[[1]]), "::", as.character(function_args[[2]]))
    }
    else {
      function_name <- if (length(function_name) == 1) {
        as.character(function_name)
      }
      else {
        canonic_expr(function_name)
      }
      return(str_c(str_c(function_name, collapse = ", "), "(", str_c(res, collapse = ", "), ")"))
    }
  }
  else if (is.symbol(exp)) {
    return("VAR")
  }
  else if (is.expression(exp)) {
    return(str_c(map(exp, canonic_expr), collapse = ", "))
  }
  else if (typeof(exp) %in% c("integer", "double", "complex")) {
    return("NUM")
  }
  else if(typeof(exp) == "logical") {
    return("BOOL")
  }
  else if(typeof(exp) == "character") {
    return("STR")
  }
  else {
    return(deparse1(exp))
  }
}

>>>>

str_op <- c("paste", "paste0", "str_c")

canonic_expr <- function(exp) {
  if (is.call(exp)) {
    function_name <- exp[[1]]
    function_args <- exp[-1]
    res <- map(function_args, canonic_expr)
    # Function_name can be larger than one is a function with a namespace stats::model or another higher-order function
    # For instance, (function(x, y) x + y)(3, 4)
    if (length(function_name) == 1 && as.character(function_name) %in% arith_func && every(res, function(v) {
      v == "NUM"
    })) {
      return("NUM")
    }
    else if (length(function_name) == 1 && as.character(function_name) %in% str_op && every(res, function(v) {
      v == "STR"
    })) {
      return("STR")
    }
    else if (length(function_name) == 1 && function_name == "::") {
      str_c(as.character(function_args[[1]]), "::", as.character(function_args[[2]]))
    }
    else {
      function_name <- if (length(function_name) == 1) {
        as.character(function_name)
      }
      else {
        canonic_expr(function_name)
      }
      return(str_c(str_c(function_name, collapse = ", "), "(", str_c(res, collapse = ", "), ")"))
    }
  }
  else if (is.symbol(exp)) {
    return("VAR")
  }
  else if (is.expression(exp)) {
    return(str_c(map(exp, canonic_expr), collapse = ", "))
  }
  else if (typeof(exp) %in% c("integer", "double", "complex")) {
    return("NUM")
  }
  else if(typeof(exp) == "logical") {
    return("BOOL")
  }
  else if(typeof(exp) == "character") {
    return("STR")
  }
  else {
    return(deparse1(exp))
  }
}
